An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-18 Report/paper.tex
finally

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
    \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ calculateXaxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ calculateYoverlap $contour1$, $contour2$
    \STATE $avgWidth =$ getAverageWordWith $text$
    \IF{ 
    $xGap < avgWidth $ \\ $* (1 / (averageCharacterCount * 2))$ \\  {\bfseries and} \\ $yOverlap > min(contour1.height, contour2.height)$ \\ $*  requiredYaxisOverlap $ 
    }
    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
The chosen paramters are:
\\
$averageCharacterCount = 8$ 
\\
$requiredYaxisOverlap = 1/2$
\end{algorithm}

@@

The text to word segmentation process can be improved upon and made more robust.
Advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements.
Algorithms that provide better noise reduction can be added to handle text images with more noise,
and experiments with rotations of the text can provide us with a more robust system to tackle text images containing heavily slanted text lines.

>>>>

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
    \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ calculateXaxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ calculateYoverlap $contour1$, $contour2$
    \STATE $avgWidth =$ getAverageWordWith $text$
    \IF{ 
    $xGap < avgWidth * (1 / 8 * 2)$ \\  {\bfseries and} \\ $yOverlap > min(contour1.height, contour2.height) / 2 $ 
    }
    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
\end{algorithm}

@@

The text to word segmentation process can be improved upon and made more robust.
Advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements.
A comparison of different text segmentation techniques is done by \cite{textsegm}.

The character segmentation process can be improved upon by increasing the accuracy of the used neural network, and by adding more techniques to remove incorrect segmentations. Several such rule-based techniques are explored in \cite{segmtechniques}.
